\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[left=6.1cm,top=2cm,right=1.5cm,bottom=1.5cm,nohead]{geometry}





\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Lucy's Updates
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}

% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage[explicit]{titlesec}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\usepackage{xcolor}
\usepackage{xifthen}


\definecolor{white}{RGB}{255,255,255}

\definecolor{darkgray}{HTML}{333333}
\definecolor{gray}{HTML}{4D4D4D}
\definecolor{lightgray}{HTML}{999999}

\definecolor{green}{HTML}{C2E15F}
\definecolor{orange}{HTML}{FDA333}
\definecolor{purple}{HTML}{D3A4F9}
\definecolor{red}{HTML}{FB4485}
%\definecolor{blue}{HTML}{6CE0F1}
\definecolor{blue}{HTML}{26D1EA}



\colorlet{fillheader}{gray}
\colorlet{header}{white}
\colorlet{textcolor}{gray}
\colorlet{headercolor}{gray}



\usepackage[]{fontspec}


\usepackage[math-style=TeX,vargreek-shape=unicode]{unicode-math}

\newfontfamily\bodyfont[]{Helvetica Neue}
\newfontfamily\thinfont[]{Helvetica Neue UltraLight}
\newfontfamily\headingfont[]{Helvetica Neue Condensed Bold}
\color{gray}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Mapping=tex-text, Color=textcolor]{Helvetica Neue Light}

\newcounter{colorCounter}
\def\@sectioncolor#1#2#3{%
  {%
    \color{%
      \ifcase\value{colorCounter}%
        blue\or%
        red\or%
        orange\or%
        green\or%
        purple\or%
        blue\or%
        red\else%
        headercolor\fi%
    } #1#2#3%
  }%
  \stepcounter{colorCounter}%
}


\renewcommand{\section}[1]{
  \par\vspace{\parskip}
  {%
    \LARGE\headingfont\color{headercolor}%
     \@sectioncolor #1%
  }
  \par\vspace{\parskip}
}


\usepackage[absolute,overlay]{textpos}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}
\newenvironment{aside}{%
  \let\oldsection\section
  \renewcommand{\section}[1]{
    \par\vspace{\baselineskip}{\Large\headingfont\color{headercolor} ##1}
  }
  \begin{textblock}{3.6}(1.5, 4.33)
  \begin{flushright}
  \obeycr
}{%
  \restorecr
  \end{flushright}
  \end{textblock}
  \let\section\oldsection
}

\usepackage{hyperref}
\usepackage{tikz}

\newcommand{\rolefont}{%
  \fontsize{14pt}{24pt}\selectfont%
  \thinfont%
  \color{white}%
}

\newcommand{\header}[3]{%
  \begin{tikzpicture}[remember picture,overlay]
    \node [rectangle, fill=fillheader, anchor=north, minimum width=\paperwidth, minimum height=4cm] (box) at (current page.north){};
    \node [anchor=center] (name) at (box) {%
      \fontsize{40pt}{72pt}\color{header}%
      {\thinfont #1}{\bodyfont  #2}
    };
    \node [anchor=north] at (name.south) {%
      \fontsize{14pt}{24pt}\color{header}%
      \thinfont #3%
    };
  \end{tikzpicture}
  \vspace{2.5cm}
  \vspace{-2\parskip}
}

\newcommand{\fn}[1]{
\hfill {\small\addfontfeature{Color=lightgray} #1}
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\footnotesize \addfontfeature{Color=lightgray}Created by Lucy in RMarkdown, inspired by the LaTeX \href{http://www.latextemplates.com/template/friggeri-resume-cv}{Friggeri} template.}

\usepackage{tabto}
\parindent0em\parskip1em
\usepackage{tikzsymbols}
\begin{document}
\pagenumbering{gobble}
\header{Lucy}{D'Agostino McGowan}{\href{mailto:}{\href{mailto:ld.mcgowan@vanderbilt.edu}{\nolinkurl{ld.mcgowan@vanderbilt.edu}}}} 

\begin{aside}
\section{contact}
2525 West End 11000 Nashville, TN 37203
\section{website}
\href{www.lucymcgowan.com}{www.lucymcgowan.com}
\section{twitter}
\href{http://twitter.com/LucyStats}{LucyStats}
\section{github}
\href{http://github.com/LucyMcGowan}{LucyMcGowan}
\section{orcid}
\href{http://orcid.org/0000-0001-7297-9359}{0000-0001-7297-9359}
\section{languages}
proficient Italian literary, written, \& oral skills
\section{programming}
\textbf{dev:} R \textbf{use:} R, SAS, Stata, Python, ArcGIS 
\section{defining attributes}
goal-driven leadership, advanced analytic skills, strategic thinking,
resourceful team player, sunny disposition \(\Springtree\), public
speaking, organizational \& communication skills
\end{aside}

\section{Interests}
\vspace{-0.25cm}
propensity score analyses, \texttt{R} package development, observational
study methods, predictive modeling, large-scale inference,
\href{https://rladies.org}{R-Ladies}, engaging beginners in \texttt{R}
package development with \href{http://ropensci.org}{rOpenSci} through
\href{https://github.com/LucyMcGowan/contributr}{\texttt{contributr}},
disparities research, community-based participatory research

\section{Education}
\vspace{-0.25cm}
    \textbf{PhD} Student in Biostatistics, GPA 3.95 \fn{Vanderbilt University}\\
     \\
    \textbf{MS} in Biostatistics, December 2013, GPA 3.88 \fn{Washington University School of Medicine}\\
         Thesis: \emph{Quantitative Assessment of the Community Research Fellows
     Training Program}\\
      \\
    \textbf{BA} with Distinction and Highest Honors \fn{University of North Carolina at Chapel Hill}\\
         Religious Studies: GPA 3.92 Romance Languages: GPA 3.86\\
      \\
\vspace{-0.85cm}
\section{Research Experience}
\vspace{-0.25cm}
\setlength{\tabcolsep}{0pt}
 \begin{tabular}{p{3.25cm} p{10.25cm}}
March 2017-present &{\textbf{RStudio}, upcoming internship under Jenny Bryan}
\end{tabular}\\
 \begin{tabular}{p{3.25cm} p{10.25cm}}
2016-2017 &{\textbf{Vanderbilt University}, NIH Big Data to Knowledge Training Fellow}
\end{tabular}\\
 \begin{tabular}{p{3.25cm} p{10.25cm}}
2015-2016 &{\textbf{Vanderbilt University}, Research Assistant, Department of Biostatistics and VA Tennessee Valley}
\end{tabular}\\
 \begin{tabular}{p{3.25cm} p{10.25cm}}
Summer 2015 &{\textbf{Cleveland Clinic}, Graduate Fellow, Department of Quantitative Health Sciences}
\end{tabular}\\
 \begin{tabular}{p{3.25cm} p{10.25cm}}
2012-2014 &{\textbf{Washington University School of Medicine}, Statistical Data Analyst promoted from Research Assistant, Department of
Surgery, Division of Public Health Sciences}
\end{tabular}\\

\vspace{-0.5cm}
\section{Awards}
\vspace{-0.25cm}
\TabPositions{1.5cm}
    2016 \tab{First Place, GSS Student Data Challenge, ASA Joint Statistical Meeting} \\
    2016 \tab{Second Place, SPAAC Poster Competition, ASA Joint Statistical Meeting} \\
    2016 \tab{Southern Startup Internship Program in Data Science (South BDHub)} \\
    2015 \tab{First Place, GSS Student Data Challenge, ASA Joint Statistical Meeting} \\
    2013 \tab{Best Contributed Paper in the Statistics and Data Analysis SAS Global
Forum} \\
    2013 \tab{First Place, Student Research Competition, 141st APHA Annual Meeting} \\
    2013 \tab{Ellis R. Ott Scholarship: ASQ Statistics Division} \\
    2012 \tab{Gertrude M. Cox Scholarship for Women in Statistics Honorable Mention} \\

\vspace{-0.5cm}
\section{Outreach}
\vspace{-0.25cm}
\TabPositions{2cm}
    2016-2017 \tab{R-Ladies Nashville, co-founder} \\
    2016-2017 \tab{Vanderbilt Graduate Student Council, President} \\
    2016-2017 \tab{Vanderbilt Biostatistics Graduate Student Association, Vice President} \\
    2016-2017 \tab{Nashville ASA Student Chapter, Vice President} \\
    2015-2017 \tab{Tennessee Office of Refugees, Tutor} \\
    2015 \tab{Scholarship of Teaching and Learning, Scholar} \\
    2014-2015 \tab{Vanderbilt Graduate Student Council, VP of Social Affairs} \\
\newgeometry{left=2cm,top=2cm,right=2cm,bottom=2cm}

\section{Select Invited
Presentations}\label{select-invited-presentations}

\vspace{-0.5cm}

\textbf{SAS Global Forum 2016} \fn{Oral Presentation}

\begin{quote}
\textbf{Lucy D'Agostino McGowan}, Robert A. Greevy, Jr
\href{http://support.sas.com/resources/papers/proceedings16/11420-2016.pdf}{``Integrating
SAS and R to Perform Optimal Propensity Score Matching.''}
\end{quote}

\textbf{SAS Global Forum 2015} \fn{Oral Presentation}

\begin{quote}
\textbf{Lucy D'Agostino McGowan}, Alice Toll
\href{http://support.sas.com/resources/papers/proceedings15/3320-2015.pdf}{``Using
PROC SURVEYREG and PROC SURVEYLOGISTIC to Assess Potential Bias.''}
\end{quote}

\section{Select Contributed
Presentations}\label{select-contributed-presentations}

\vspace{-0.5cm} \textbf{ENAR 2017} \fn{Oral Presentation}

\begin{quote}
\textbf{Lucy D'Agostino McGowan}, Robert Alan Greevy, Jr, ``Simplifying
and Contextualizing Sensitivity to Unmeasured Confounding Tipping Point
Analyses.''
\end{quote}

\textbf{ASA Joint Statistical Meeting 2016} \fn{Poster}

\begin{quote}
\textbf{Lucy D'Agostino McGowan}, Robert A. Greevy, Jr, ``Practical
Guidance and Tools for Rule-Out Sensitivity to Unmeasured Confounding
Analyses.''
\end{quote}

\section{Peer-reviewed Publications}\label{peer-reviewed-publications}

\vspace{-0.5cm}

\hypertarget{refs}{}
\hypertarget{ref-McGowan:2016ira}{}
\textbf{D'Agostino McGowan, Lucy}, Bullen, J. A., \& Obuchowski, N. A.
(2016). Location Bias in ROC Studies. \emph{Statistics in
Biopharmaceutical Research}, 00--00.

\hypertarget{ref-Drake:2016ks}{}
Drake, B. F., Brown, K., \textbf{D'Agostino McGowan, Lucy},
Haslag-Minoff, J., \& Kaphingst, K. (2016). Secondary consent to
biospecimen use in a prostate cancer biorepository. \emph{BMC Research
Notes}, \emph{9}(1), 346.

\hypertarget{ref-Kaphingst:2015kl}{}
Kaphingst, K. A., Stafford, J. D., \textbf{D'Agostino McGowan, Lucy},
Seo, J., Lachance, C. R., \& Goodman, M. S. (2015). Effects of racial
and ethnic group and health literacy on responses to genomic risk
information in a medically underserved population. \emph{Health
Psychology}, \emph{34}(2), 101--110.

\hypertarget{ref-Chen:2015ki}{}
Chen, Y.-H., \textbf{D'Agostino McGowan, Lucy}, Cimino, P. J., Dahiya,
S., Leonard, J. R., Lee, D. Y., \& Gutmann, D. H. (2015). Mouse
Low-Grade Gliomas Contain Cancer Stem Cells with Unique Molecular and
Functional Properties. \emph{Cell Reports}, \emph{10}(11), 1899--1912.

\hypertarget{ref-McGowan:2015bt}{}
\textbf{D'Agostino McGowan, Lucy}, Stafford, J. D., Thompson, V. L.,
Johnson-Javois, B., \& Goodman, M. S. (2015). Quantitative Evaluation of
the Community Research Fellows Training Program. \emph{Frontiers in
Public Health}, \emph{3}(1), 11.

\hypertarget{ref-Fisher:2014jt}{}
Fisher, M. J., Loguidice, M., Gutmann, D. H., Listernick, R., Ferner, R.
E., Ullrich, N. J., \ldots{} Liu, G. T. (2014). Gender as a disease
modifier in neurofibromatosis type 1 optic pathway glioma. \emph{Annals
of Neurology}, \emph{75}(5), 799--800.

\hypertarget{ref-Griffey:2014fa}{}
Griffey, R. T., Kennedy, S. K., \textbf{D'Agostino McGowan, Lucy},
Goodman, M., \& Kaphingst, K. A. (2014). Is low health literacy
associated with increased emergency department utilization and
recidivism? \emph{Academic Emergency Medicine : Official Journal of the
Society for Academic Emergency Medicine}, \emph{21}(10), 1109--1115.

\hypertarget{ref-DiggsAndrews:2014fb}{}
Diggs-Andrews, K. A., Brown, J. A., Gianino, S. M., \textbf{D'Agostino
McGowan, Lucy}, Rubin, J. B., Wozniak, D. F., \& Gutmann, D. H. (2014).
Reply. \emph{Annals of Neurology}, \emph{75}(5), 800--801.

\hypertarget{ref-Colditz:2014hh}{}
Colditz, G. A., \textbf{D'Agostino McGowan, Lucy}, James, A. S., Bohlke,
K., \& Goodman, M. S. (2014). Screening for colorectal cancer: using
data to set prevention priorities. \emph{Cancer Causes \& Control :
CCC}, \emph{25}(1), 93--98.

\hypertarget{ref-DAgostinoMcGowan:2013ew}{}
\textbf{D'Agostino McGowan, Lucy}, Gennarelli, R., Lyons, S., \&
Goodman, M. (2013). Using Small-Area Analysis to Estimate County-Level
Racial Disparities in Obesity Demonstrating the Necessity of Targeted
Interventions. \emph{International Journal of Environmental Research and
Public Health}, \emph{11}(1), 418--428.

\end{document}
